Fractional Types

### 2013-02-25 frac.tex
_

  \dgm{delimc-times}
\end{multicols}
\noindent Dually, as illustrated above on the right, we also have a
{{coname}} combinator which when given an answer {{v2 : b2}}, and a request
for the corresponding input {{1/b1}} for {{c : b1 <-> b2}}, eliminates this
as a un-needed computation.

@@

@@

For these reasons, it is interesting to consider other possible semantic
interpretations of fractionals. A natural alternative is to use the
``canonical'' compact closed category, that is finite dimensional vector
spaces and linear
maps~\cite{Selinger:2011:FDH:1942319.1942398,hasegawa2008finite}
over fields of characteristic $0$ (or even the category of finite dimensional
Hilbert spaces). Let us fix an arbitrary field $k$ of characteristic $0$.
Then each type {{b}} in {{PiTF}} is interpreted as a finite dimensional
vector space $\mathbf{V}_b$ over the field $k$. In particular:
\begin{itemize}
  \item every vector space contains a zero vector which means that the type
    {{0}} (if included in {{PiTF}}) would not be the ``empty'' type.
    Furthermore all combinators would be
    strict as they would have to map the zero vector to itself. 
  \item the type {{1}} is interpreted as a 1-dimensional vector space and hence
    is isomorphic to the underlying field.
  \item the fractional type {{1/b}} is interpreted as the dual vector space
    to the vector space $\mathbf{V}_b$ representing {{b}} consisting of all
    the \emph{linear functionals} on $\mathbf{V}_b$.
  \item one can then validate certain desirable properties: {{1/(1/b)}} is
    isomorphic to~{{b}}; and {{eps*_b}} corresponds to a bilinear form which
    maps a dual vector and a vector to a field element.
\end{itemize}
In such categories, the fractional type is given a non-trivial
interpretation. Indeed, while the space of column vectors is isomorphic to
the space of row vectors, they are nevertheless quite different, being
$(1,0)$ and $(0,1)$ tensors (respectively).  In other words, the category
provides a more refined model in which isomorphic negative-information values
and positive-information are not identified.

@@

@@

>>>>

  \dgm{delimc-times}
\end{multicols}
\noindent Dually, as illustrated above on the right, we also have a
{{coname}} combinator which when given an answer {{v2 : b2}}, and a request
for the corresponding input {{1/b1}} for {{c : b1 <-> b2}}, eliminates this
as a un-needed computation (see also Sec. 3, \cite{abramsky-2008}).

@@

\roshan{Either we should have explain the SAT solver well or we
  shouldn't have at all. There are some original ideas in the
  construction of that solver and the Oxford QF group for instance
  were very interested in its details. This presentation neither
  leaves the idea prime for future publication, and neither does it
  explain it well.}

@@

For these reasons, it is interesting to consider other possible semantic
interpretations of fractionals. A natural alternative is to use the
``canonical'' compact closed category, that is finite dimensional vector
spaces and linear
maps~\cite{Selinger:2011:FDH:1942319.1942398,hasegawa2008finite}
over fields of characteristic $0$ (or even the category of finite dimensional
Hilbert spaces). Let us fix an arbitrary field $k$ of characteristic $0$.
Then each type {{b}} in {{PiTF}} is interpreted as a finite dimensional
vector space $\mathbf{V}_b$ over the field $k$. In particular:
\begin{itemize}
  \item every vector space contains a zero vector which means that the type
    {{0}} (if included in {{PiTF}}) would not be the ``empty'' type.
    Furthermore all combinators would be
    strict as they would have to map the zero vector to itself. 
  \item the type {{1}} is interpreted as a 1-dimensional vector space and hence
    is isomorphic to the underlying field.
  \item the fractional type {{1/b}} is interpreted as the dual vector space
    to the vector space $\mathbf{V}_b$ representing {{b}} consisting of all
    the \emph{linear functionals} on $\mathbf{V}_b$.
  \item one can then validate certain desirable properties: {{1/(1/b)}} is
    isomorphic to~{{b}}; and {{eps*_b}} corresponds to a bilinear form which
    maps a dual vector and a vector to a field element.
\end{itemize}

\roshan{Again, if we have lost zero, we cannot talk about vector
  spaces with the zero vector. We should alternately included it in
  our presentation to start with. }

In such categories, the fractional type is given a non-trivial
interpretation. Indeed, while the space of column vectors is isomorphic to
the space of row vectors, they are nevertheless quite different, being
$(1,0)$ and $(0,1)$ tensors (respectively).  In other words, the category
provides a more refined model in which isomorphic negative-information values
and positive-information are not identified.

@@

\roshan{The above para should simply be deleted.}

@@

\roshan{Again, the above para is just lose speculation. Further, the
  fact that we say that its cartesian closed instead of monoidal
  closed should *immediately* tell us that its the wrong model.}
